---
title: "Table Calculations"
output: html_notebook
---

# TABLE CALCULATIONS

## n

```{r}
neomod %>%
  filter(cns == "1")
```

```{r}
neomod %>%
  filter(cns == "0")
```

## birth weight

```{r}
neomod %>%
  filter(cns == "1") %>%
  summarise(mean = mean(bwt))

```

```{r}
neomod %>%
  filter(cns == "0") %>%
  summarise(mean = mean(bwt))

```

## gestation

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(gest)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(gest)
```


## gender

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(sex)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(sex)
```

## mother employment

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(emp.f)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(emp.f)
```
 
 
## father employment

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(emp.m)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(emp.m)
```

## education age

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(edu)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(edu)
```

## accomodation

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(accom)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(accom)
```

## nnu size

```{r}
neomod %>%
  filter(cns == "0") %>%
  count(size)
```

```{r}
neomod %>%
  filter(cns == "1") %>%
  count(size)
```

new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
